%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemDot}[2]{
  \item\small{
    \textbf{#1}{. #2 \vspace{-2pt}}
  }
}

\newcommand{\resumePub}[1]{
  \item\small{#1 \vspace{-2pt}}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://yoon.ws}{\Large Wonsup Yoon}} & Email : \href{mailto:wsyoon@kaist.ac.kr}{wsyoon@kaist.ac.kr}\\
  Ph.D. Student, KAIST  & \href{https://yoon.ws}{https://yoon.ws} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{KAIST}{Republic of Korea}
{Ph.D. in Computer Science}{Sep. 2019 -- Aug. 2025 (expected)}
\resumeItemListStart
\resumeItem{Co-advisors}{Sue Moon and Youngjin Kwon.}
\resumeItemListEnd
\resumeSubheading
{KAIST}{Republic of Korea}
{M.S. in Computer Science}{Sep. 2017 -- Aug. 2019}
\resumeItemListStart
\resumeItem{Co-advisors}{Sue Moon and Youngjin Kwon.}
\resumeItem{Thesis title}{A Memory Management Layer for Disaggregated Data Center.}
\resumeItemListEnd
\resumeSubheading
{Yonsei University}{Republic of Korea}
{B.S. in Electrical and Electronic Engineering;  GPA: 4.01/4.30}{Mar. 2013 -- Feb. 2017}
\resumeItemListStart
\resumeItem{Minor}{Computer Science}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Advanced Networking Lab, KAIST}{Republic of Korea}
{Teaching Assistant}{2017 - 2022, 2024}
\resumeItemListStart
\resumeItemDot{Introduction to Computer Networks (CS341)}
{Taught and developed KENS (KAIST Educational Network System) project assignments. Worked on extending KENS for memory safety, build system, development environment, and teaching ecosystem.}
\resumeItemDot{Distributed Algorithms and Systems (CS443)}
{Taught Raft consensus algorithm project assignments.}
\resumeItemDot{Graduate Operating Systems (CS530)}
{Taught operating system project assignments based on OSv unikernel.}
\resumeItemListEnd

\resumeSubheading
{Institute of Language and Information Studies, Yonsei University}{Republic of Korea}
{Technical Assistant and Software Developer}{2013 - 2017}
\resumeItemListStart
\resumeItemDot{Yonsei Corpus Searcher}
{Developed efficient a search-filter-sort application for the Yonsei Korean corpus.}
\resumeItemDot{Yonsei Dictionary Searcher}
{Developed efficient web-based and .net-based search applications for the Yonsei Korean dictionary.}
\resumeItemDot{Dictionary searcher for the National Institute of Korean Language}
{Developed a dictionary search web application for Korean language.}
\resumeItemDot{TOPIK Word Searcher for National Institute for International Education}
{Developed an education-level-based dictionary search application used for TOPIK (Test Of Proficiency In Korean).}
\resumeItemListEnd


\resumeSubHeadingListEnd


\section{Research Interest}

My broad research interests are:
\resumeSubHeadingListStart
\resumeItem{Virtualization}{unikernels, microVM, and containers.}
\resumeItem{Networking}{RDMA, virtio, and programmable NICs.}
\resumeItem{Datacenter}{resource disaggregation, microsecond-scale systems, and tail-optimized systems.}
\resumeSubHeadingListEnd




%-----------AWARD-----------------
\section{Awards and Honors}
\resumeSubHeadingListStart
%%% pusnow award start %%%
\resumeSubheading {SIGCOMM '23 Travel Grants (USD 1500)}{ACM SIGCOMM}{Awarded for travel to present at the ACM SIGCOMM 2023 conference.}{Sep. 2023}
\resumeSubheading {Best Paper Award}{APNet'23}{Awarded for the paper ``Host Efficient Networking Stack Utilizing NIC DRAM''.}{Jun. 2023}
\resumeSubheading {Best TA Award}{KAIST}{Awarded for teaching the class Introduction to Computer Networks (CS341).}{Jul. 2021}
\resumeSubheading {Awarded High Honors (Top 3\%)}{Yonsei University}{Awarded for outstanding performance in coursework.}{Aug. 2016 and Feb. 2017}
\resumeSubheading {The National Scholarship for Science and Engineering}{Korea Student Aid Foundation}{Awarded for outstanding performance in coursework.}{Dec. 2015 and Sep. 2016}
\resumeSubheading {Yonsei Internal Scholarship}{Yonsei University}{Awarded for outstanding performance in coursework.}{Sep. 2015 and Mar. 2016}
\resumeSubheading {Awarded Honors (Top 10\%)}{Yonsei University}{Awarded for outstanding performance in coursework.}{Feb. 2015, Aug. 2015, and Feb. 2016}
\resumeSubheading {Korea Telecom Scholarship}{Korea Telecom}{Awarded for outstanding performance in coursework.}{Aug. 2015}
%%% pusnow award end %%%
\resumeSubHeadingListEnd


%-----------PUBLICATION-----------------
\section{Publications}
\resumeSubHeadingListStart
%%% pusnow publication start %%%
\resumePub{\textbf{Wonsup Yoon}, Jisu Ok, Sue Moon, and Youngjin Kwon. Adios to Busy-Waiting for Microsecond-scale Memory Disaggregation. In \textit{Proceedings of the Twentieth European Conference on Computer Systems (EuroSys).} 2025.}
\resumePub{Gangmin Lee, \textbf{Wonsup Yoon}, and Sue Moon. Dynamic Dispatcher Assignment With Flat-Combining. In \textit{Proceedings of the Twentieth European Conference on Computer Systems (Poster Session) (EuroSys '25 Posters).} 2025.}
\resumePub{Jisu Ok, \textbf{Wonsup Yoon}, and Sue Moon. Poster: Pushing RDMA into Milliseconds RTT Communication. In \textit{Proceedings of the 20th International Conference on emerging Networking EXperiments and Technologies (Poster Session) (CoNEXT '24 Posters).} 2024.}
\resumePub{\textbf{Wonsup Yoon}, Jisu Ok, Sue Moon, and Youngjin Kwon. Poster: Designing a Memory Disaggregation System for Cloud. In \textit{Proceedings of the ACM SIGCOMM 2023 Conference Posters and Demos (SIGCOMM '23 Posters and Demos).} 2023.}
\resumePub{Byeongkeon Lee, Donghyeon Lee, Jisu Ok, \textbf{Wonsup Yoon}, and Sue Moon. Host Efficient Networking Stack Utilizing NIC DRAM. In \textit{Proceedings of the 7th Asia-Pacific Workshop on Networking (APNet).} 2023.}
\resumePub{\textbf{Wonsup Yoon}, Jisu Ok, Jinyoung Oh, Sue Moon, and Youngjin Kwon. DiLOS: Do Not Trade Compatibility for Performance in Memory Disaggregation. In \textit{Proceedings of the Eighteenth European Conference on Computer Systems (EuroSys).} 2023.}
\resumePub{\textbf{Wonsup Yoon}, Jinyoung Oh, Jisu Ok, Sue Moon, and Youngjin Kwon. DiLOS: adding performance to paging-based memory disaggregation. In \textit{Proceedings of the 12th ACM SIGOPS Asia-Pacific Workshop on Systems (APSys).} 2021.}
\resumePub{\textbf{Wonsup Yoon}, Jinyoung Oh, Sue Moon, and Youngjin Kwon. Accelerating disaggregated data centers using unikernel. In \textit{Proceedings of the ACM SIGCOMM 2020 Conference Posters and Demos (SIGCOMM '20 Posters and Demos).} 2020.}
\resumePub{Keunhong Lee, Jeehoon Kang, \textbf{Wonsup Yoon}, Joongi Kim, and Sue Moon. Enveloping Implicit Assumptions of Intrusive Data Structures within Ownership Type System. In \textit{Proceedings of the 10th Workshop on Programming Languages and Operating Systems (PLOS@SOSP).} 2019.}
%%% pusnow publication end %%%
\resumeSubHeadingListEnd



%--------TALKS------------
\section{Invited Talks}
\resumeSubHeadingListStart
%%% pusnow talk start %%%
\resumeSubheading{Efficient Memory Disaggregation Systems Using Unikernel}{KIISE KCC}{Invited for doctorial forum.}{2024}
\resumeSubheading{DiLOS: Do Not Trade Compatibility for Performance in Memory Disaggregation}{KIISE KCC}{Invited for top conference session.}{2024}
\resumeSubheading{DiLOS: Do Not Trade Compatibility for Performance in Memory Disaggregation}{Samsung GTS}{Invited for the Samsung Global Technology Symposium.}{2023}
\resumeSubheading{Designing a Latency-Optimized Scheduler for Memory Disaggregation}{EuroDW}{Invited for the 17th EuroSys doctoral workshop.}{2023}
%%% pusnow talk end %%%
\resumeSubHeadingListEnd

%--------PROFESSIONAL ACTIVITIES------------
\section{Professional Activities}
\resumeSubHeadingListStart
%%% pusnow activity start %%%
\resumeSubheading{EuroSys'22 Shadow PC}{EuroSys}{Served as a member of a shadow PC.}{2022}
%%% pusnow activity end %%%
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}